---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggmemory

<!-- badges: start -->
<!-- badges: end -->

The goal of ggmemory is to present code and output as it was executed in an interactive session; support is currently focused on data manipulation pipelines and data visualization.

---

# How.

- Code is harvested from the history.  This can be done via RStudio IDE or other means like `savehistory("temp_history.R")`.

- Then the user can format the code to respect indentation conventions for pipelines.  Recommended is using RStudio and `rstudioapi::executeCommand("reformatCode")` or menu options to do the same. *On wish list is to do this reformatting step programmatically formatR::tidy_source() seems promising, but does not work on code containing errors.  Error free code for interactive sessions does not seem realistic*.

- Then, the ggmemory function `r_code_extract_code_list` can be used on the reformated .R file containing the history.  This function further parses code into a list containing individual pipelines or single lines of code based on indentation that compose the entire history. 

```{r}
library(magrittr)
'library(ggplot2)
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "magenta")
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "magenta",
             size = 8)
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "magenta",
             size = 8,
             alpha = .5)' %>% 
  ggmemory::r_code_extract_code_list(code = .)
```



- Finally, this list with the code sequence can be entered as an argument to the function `chunk_reveal` from the {flipbookr} package, used with {xaringan}.  Each slide in the Xaringan slide show will display a code execution moment of the interactive session by the user.  
  `
```{r}
'library(ggplot2)
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "magenta")
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(color = "magenta",
             size = 8)' %>% 
  ggmemory::r_code_extract_code_list(code = .) ->
my_executions
```

`flipbookr::chunk_reveal(code_seq = my_executions)`

- A template is provided with the ideal set up for the {xaringan} slides; i.e. `error = TRUE`

*Steps 3-5 might be bundled up in the future.*

# Precidents and Motivation.

flipbookr was designed to present curated code pipelines or code experiences (rotating arguments).  Consumers can see how you might build up a chart or data manipulation pipeline.  However, the experiences are rather curated, and not true to how data manipulation is actually conduction -- probably not as linear as the 'classic flipbookr' presentations. 

Moreover, action *within lines* -- for example changing color of a point geom or size: geom_point() -> geom_point(size = 12) -- is tricky to demonstrate using classic {flipbookr} presentations.  Motivation for working on {memory} are other packages, whose within-line changes are where important points of decision: {ggstamp} and {ggsample}.

## Related work.

{camcorder} is a package that seeks to capture all *data visualizations* produced in an interactive session.  These are then reproduced together in a gif.  The package's focus is on evolution of the output rather than translation between code and output.  The strategy to achieve this too, is fairly different from {memory}.


